\cvsection{Experience}
\begin{cventries}
  \cventry
    {Investment assistant}
    {Addor Capital}
    {Nanjing, China}
    {May. 2021 - Jun. 2021}
    {
      \begin{cvitems}
        \item {Risk management during financial due diligence}
        \item {Cyber Range industry performance data quantitative model and  analysis}
        \item {C-suite interviews and company profiling}
      \end{cvitems}
    }



  \cventry
    {Project manager \& Coder}
    {Shunzhi Tech Inc.}
    {Nanjing, China}
    {Jun. 2020 - Sep. 2020}
    {
      \begin{cvitems}
        \item {Designed a change detection model on VHR satellite pictures(34\% better than benchmark)}
        \item {Implemented real-time video stream object detection project}
        \item {Heterogeneous computing analysis and development on multiple service providers}
      \end{cvitems}
    }

  \cventry
    {Software Engineer}
    {Freelance software development}
    {Online}
    {Jun. 2015 - PRESENT}
    {
      \begin{cvitems}
        \item {(In progress)A quantitative trading PaaS for user benchmarking against AI}
        \item {(In progress)ESG fund voting pattern research}
        \item {A face-emotion based lie detector using UNet framework}
        \item {Project Seichi, a place-of-interest GIS with React.js}
      \end{cvitems}
    }

  \cventry
    {Consultant}
    {Consulting with Frauenmond, TBM Inc.}
    {Seoul, Korea}
    {Oct. 2019 - Dec. 2019}
    {
      \begin{cvitems}
        \item {Analyzed Korean chocolate market with Porter's Five Forces Model and managerial accounting}
        \item {Strategized with Encouragement Study based on Genetic Matching and Regression Discontinuity}
        \item {Offered Neural Network model for Alpha/Beta tests on feature designing}
      \end{cvitems}
    }

  \cventry
    {Project manager \& Coder}
    {Project Safe Francisco with Gensler Inc.}
    {San Francisco, United States}
    {Sep. 2018 - May. 2019}
    {
      \begin{cvitems}
        \item {Developed a San Francisco simulation game, chosen as showcase project}
        \item {Scripted game events based on interviews and surveys}
        \item {Continuous intergration with Gensler Inc. and their architecture designing team}
      \end{cvitems}
    }

  \cventry
    {Web developer \& Component designer}
    {Nine Chapter Inc.}
    {Shanghai, China}
    {Aug. 2017 - Nov. 2017}
    {
      \begin{cvitems}
        \item {Streamlined frontend building process}
        \item {20x speedup for project building with caching design}
        \item {Bridged major front-to-back communications \& REST API design}
      \end{cvitems}
    }

  \cventry
    {Group leader \& Coder}
    {Complex Network at the University of Pennsylvania}
    {Philadelphia, United States}
    {Jul. 2016 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Analyzed social/bio network with stochastic simulation}
        \item {Implemented PageRank under a distribution network setting}
        \item {200x speedup in a month's iteration}
      \end{cvitems}
    }

  %% \cventry
  %%   {Image Analyzer \& Asteroid Researcher}
  %%   {IASC Asteroid Search}
  %%   {Wuxi, China}
  %%   {Jun. 2015 - Oct. 2015}
  %%   {
  %%     \begin{cvitems}
  %%       \item {Analyzed images for possible unidentified asteroid with image recognizing algorithm}
  %%       \item {Reported results to Minor Planet Center, Harvard University}
  %%       \item {Located 2 asteroids based on NASA-provided images}
  %%     \end{cvitems}
  %%   }
\end{cventries}
